Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-03 docs/evol.tex
relation between jarsize and defects count

>>>>

We explored te relation between defects with the size of a project,
measured by the size of its jar file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

\begin{table}
    \centering
    \caption{Correlations between jarsize and Defects Count}
    \label{tbl:jarsizecorr}
    \input{jarsizecorr.tex}
\end{table}
